---
title: Brevoort Template
format:
  brevoort-pdf:
    keep-tex: true
    keep-md: true  
author:
  - name: Sarah Malloc
    affiliations:
      - name: An Organization
        department: The Department
        address: 1 Main St
        city: Boston
        country: USA
        postal-code: 02210-1022
      - A second affilication
    orcid: 0000-0000-0000-0000
    email: sm@example.org
    url: https://example.org/
  - name: Eliza Dealloc
    affiliations:
      - Another Affiliation
abstract: |
  This document is a template demonstrating the Brevoort format.
keywords: [template, demo]
bibliography: bibliography.bib
geometry: 
  - top=1in
  - left=1.5in
  - right=1.5in
---

```{r}
#| include: false
#| echo: false

library(tidyverse)
library(gt)

f <- function(x) {
  
  byline <- strsplit(x, '\n')[[1]]
  
  if (any(hascap <- grepl('\\\\caption', byline))) {
    afterpos <- which(hascap)
  } else if (any(haslong <- grepl('\\\\begin\\{longtable\\}', byline))) {
    afterpos <- which(haslong)
  } else afterpos <- 0L
  
  ret_val <- append(byline, 
                    '\\tablenote{This is my note which is very very very very very very very very very very very very very very very very very very very very very very very long.} \\\\ \n',
                    afterpos) %>%
    paste(collapse = '\n')
  
  class(ret_val) <- class(x)
  attributes(ret_val) <- attributes(x)
  
  ret_val
}
```

## Introduction with a very lengthy text description that will hopefully spread out over two or possibly even three lines {#sec-intro}

*TODO* Create a template that demonstrates the appearance, formatting, layout, and functionality of your format. Learn more about journal formats at <https://quarto.org/docs/journals/>. See details from @CameronTrivedi2013.

```{r}
#| label: tbl-table1
#| echo: false
#| tbl-cap:  This is the first table of many

# tbl-subcap: This is a subcaption

gt::gt(mtcars %>% dplyr::slice(1:5)) %>%
  gt::as_latex() %>%
  f()
```

Take a look at @tbl-table1.

\clearpage
singlespacing
\section*{References}

::: {#refs}
:::
